\cvsection{Selected Projects}
\begin{cventries}
  \cventry
    {Graduate Student Researcher | \textit{Numpy, PyTorch}}
    {Personalized Domain Expert Recommendation on QA Websites}
    {UCLA}
    {Aug. 2017 - Present}
    {
    	\begin{cvitems}
    		\item {Learnt the similarity between users from user network structure information and accepted-answer ranking information to provide personalized and best answering candidates for recommendation given the question proposed by a specific user.}
    		\item {Jointly optimized network embedding similarity loss between users and ranking loss amoung answers. Used Bidirectional LSTM for learning the representations of question contents.}
        % \item {Implementd the proposed algorithm in Python and PyTorch.}
    	\end{cvitems}
    }

\vspace{-1em}

  \cventry
    {Graduate Student Researcher | \textit{Java}}
    {All Case Reports with Open Biomedical Annotation Terms (ACROBAT)}
    {UCLA}
    {Jul. 2017 - Present}
    {
    	\begin{cvitems}
			\item {To implement a case report auto-annotation tool to identify the typed medical entities, relationships, and temporal information to construct graphical representation of treatment-disease development. Learn the representation of heterogeneous graphs for achieving high accuracy similarity search query and finding undocumented relationships between medical entities.}
			\item {Worked on Temporal Expression Extraction by introducing new hand-crafted rules to SUTime and collaborating with an Regex section.}
    	\end{cvitems}
    }

\vspace{-1.2em}

\cventry
  {Course Project | \textit{Python, PyTorch}}
  {Adversarial Gender-debiased Word Embedding}
  {UCLA}
  {Oct. 2017 - Dec. 2017}
  {
    \begin{cvitems}
        \item {Built an adversarial model to learn gender-debiased word embedding and extracted the invariant information by jointly encoding the gender information and the invariant and feeding the encoded to 
        \textit{Discriminator}.}
        \item {Occupation project evaluation and word analogy test show that our model indeed removed the gender stereotype and achieved gender-debiased word embedding.}
    \end{cvitems}
  }

\cventry
  {Course Project | \textit{Numpy, Sci-kit Learn}}
	{Forecasting the Best Answers in Community-based Question Answering Services}
	{UCLA}
	{Apr. 2017 - Jun. 2017}
	{
		\begin{cvitems}
			\item {Automatically predicted best answers of questions in community-based QA forum (e.g. Stack Overflow). Four types of features are employed: statistical and meta features, social network, user expertise features, and natural language features.}
			\item {Used LambdaMART, one of the state of the art learning to rank models, to learn and select the highest answer as the prediction}
			\item {Empirical results show that proposed model outperforms all baselines and enhances the 7\% of the average $P@1$.}
		\end{cvitems}
	}
%  \cventry
%    {Researcher}
%    {MRI: Customizable Computing Instrument for Large-scale Genomic Analysis}
%    {UCLA}
%    {Sept. 2016 - Present }
%    {
%      \begin{cvitems}
%        \item {Aimed at genotype imputation from low coverage genetic datasets based only on sequencing read data without sufficient reference panel and microarray data.}
%        \item {Woring on optimizing the imputation algorithm combined by a Hidden Markov Model and a EM Algorithm.}
%        \item {Working on accelerating the genotype imputation based on STITCH, a program developed by R and C++ for genotype imputation, and implementing the optimized software on a server equipped with FPGAs and GPUs.}
%      \end{cvitems}
%    }
\vspace{-1em}
  \cventry
    {Undergraduate Student Researcher}
    {Research of Basic Theory and Critical Technique on Big Data Usability}
    {HIT}
    {Mar. 2015 - Jun. 2016}
    {
      \begin{cvitems}
        \item{Focused on developing data quality concepts and data cleaning algorithms, especially on  regular-grammar-constrained data repairing techniques through pattern regular expressions.}
        \item{Proposed Regular-expression-based Structural Repair (RSR) algorithm which is a dynamic programming method with time complexity $O(nm^2)$ and space complexity $O(nm)$.}
        \item{Combined the RSR algorithm (for structural repair) with the value repair algorithm, a selection between association rule mining and edit distance. Constructed whole repairing methodology. Conducted excessive experiment to prove the effectiveness and efficiency.}
      \end{cvitems}
    }
% \vspace{-1em}
%  \cventry
%    {Compiler designer and programmer}
%    {Simple Compiler of C Programming Language}
%    {HIT}
%    {Feb. 2015 - Jun. 2015}
%    {
%        Programmed in C++. Built an elementary C program language compiler with four components: lexical analysis, grammatical analysis, and intermediate code generation. 
%    }
% \vspace{-1em}
%   \cventry
%     {Software Engineer}
%     {Conference Partner on Google Calendar}
%     {HIT}
%     {Sept. 2014 - Jan. 2015}
%     {
% 		Implemented a web application that crawls conference information (date, location, domain, etc.) from internet, parses raw data by regular expression, and inserts parsed record and stored in MySQL database into the user’s Google calendar as a reminder.
%     }

\end{cventries}
